Finding Quality Issues in SKOS Vocabularies

### 2012-03-23 background.tex
first attempt for related work section

% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency. Such quality criteria are already well-established and have extensively been discussed in standardized guidelines \cite{ISO25964-1:2011,Z39.19:2005}, manuals \cite{Hedden2010,Aitchison2000,Harpring2010}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002}.

>>>>

% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency. Such quality criteria are already well-established and have extensively been discussed in standardized guidelines \cite{ISO25964-1:2011,Z39.19:2005}, manuals \cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002}.

### 2012-03-23 criteria.tex
first attempt for related work section

% Origin and rationale
Two concepts that are explicitly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} can be regarded a quality issue because, according to \cite{SkosReference2008}, they are ``not used to make assertions''. Transitive hierarchical relations in SKOS are meant to be inferred by the vocabulary consumer, which is reflected in the SKOS schema by, e.g., \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}. 
% Function definition
We encode this issue in a function \textit{strc} that iterates over all concept pairs $C \times C$ that are directly related by the mentioned transitive properties, not by one of their subproperties.

% TODO CM: it is unclear what "mentioned" means in this context...

>>>>

% Origin and rationale
Two concepts that are explicitly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} can be regarded a quality issue because, according to \cite{SkosReference2008}, they are ``not used to make assertions''. Transitive hierarchical relations in SKOS are meant to be inferred by the vocabulary consumer, which is reflected in the SKOS schema by, e.g., \texttt{skos:broader} being a subproperty of \texttt{skos:broaderTransitive}. 
% Function definition
We encode this issue in a function \textit{strc} that iterates over all concept pairs $C \times C$ that are directly related by \texttt{skos:broaderTransitive} and/or \texttt{skos:narrowerTransitive} properties and not by one of their subproperties.
